### 2013-11-01 inst/doc/vignette.Rmd
add support for writing older eml versions, e.g. 2.1.0
tweak vignette

```{r}
obj <- eml_read("reml_example.xml")
obj 
```

@@

```{r}
dataTable(obj)
```

@@

```r
install.packages("uuid",,'http://rforge.net/',type='source')
install_github("RHTMLForms", "omegahat")
install_github("XMLSchema", "omegahat")
```

>>>>

```{r}
obj <- eml_read("reml_example.xml")
```

@@

```{r}
dat <- dataTable(obj)
```

@@

```r
install.packages("uuid")
install_github("RHTMLForms", "omegahat")
install_github("XMLSchema", "omegahat")
```
